---
title: "In Situ Phenological Data from NPN, Plot with PhenoCam"
author: "K Duffy"
date: "3/11/2020"
output: html_document
---

```{r}
library(dplyr)
library(lubridate)
library(rnpn)
```

**Use the vignettes to pull in rnpn data here for MOAB and ONAQ


If you pull in data from the npn website this is how you would want to read it in:
1.change the path to whatever is on your computer)
2.break out the data into grasses and shrubs
3.do this separetly for ONAQ versus MOAB

Example to edit for ONAQ.  This is from a different NEON site (JORN)
```{r}
df <- read.table('/Users/kdw223/Research/PostDoc/phenoSynth/Notebooks/greenwave_dacqre/npn_data/Jornada_StatusandIntensity_leaves.csv', header = TRUE, sep = ",", stringsAsFactors = FALSE)
df=df%>%
  filter(df$Intensity_Value!=-9999)
df=df%>%
  filter(df$Phenophase_Description==c('Leaves', 'Leaves (grasses)'))
df$Observation_Date=as.Date(df$Observation_Date, format="%m/%d/%Y")
xscale=data.frame(unique(df$Intensity_Value))
```

Pull out the shrub data:
```{r}

npn_SH=df%>%
  filter(Functional.Type=='shrub')%>%
  arrange(Observation_Date) %>%
  rename(date=Observation_Date) %>% rowwise() %>% dplyr::mutate(percent_int_value = strsplit(Intensity_Value, '-')[[1]][2]) %>%
  dplyr::mutate(percent_int_value = substr(percent_int_value,1,nchar(percent_int_value)-1))%>%
  dplyr::mutate(percent_int_value = as.integer(percent_int_value)) %>% ungroup() %>%
  dplyr::group_by(date) %>% dplyr::mutate(mean_status_int = mean(percent_int_value)) %>% 
  dplyr::select(mean_status_int, date, Functional.Type) %>% dplyr::distinct()
npn_SH
```
Pull out the grass data:
```{r}
npn_GR=df%>%
  filter(Functional.Type=='grass')%>%
  arrange(Observation_Date) %>%
  rename(date=Observation_Date) %>% rowwise() %>% dplyr::mutate(percent_int_value = strsplit(Intensity_Value, '-')[[1]][2]) %>%
  dplyr::mutate(percent_int_value = substr(percent_int_value,1,nchar(percent_int_value)-1)) %>%
  dplyr::mutate(percent_int_value = as.integer(percent_int_value)) %>% ungroup() %>%
  dplyr::group_by(date) %>% dplyr::mutate(mean_status_int = mean(percent_int_value)) %>% 
  dplyr::select(mean_status_int, date, Functional.Type) %>% dplyr::distinct()
  
npn_GR
```

Plot them:
```{r}

library(plotly)
p2 = plot_ly(
    data = npn_GR,
    x = ~ as.factor(npn_GR$date),
    y = ~ as.factor(npn_GR$Intensity_Value),
    showlegend = TRUE,
    type = 'bar',
     opacity = .8,
    name='Jornada NPN Grass', 
    #text=unique(df$Intensity_Value),
    marker=list(color="goldenrod", size=3)
   ) %>%
   add_trace(
      x=~as.factor(npn_SH$date),
     y=~as.factor(npn_SH$Intensity_Value),
     type = "bar",
      opacity = .5,
     name='Jornada NPN Shrubs',
     marker = list(color="royalblue", size=3)
  )
p2
```
Clean up the axes:
```{r}

p2 <- p2 %>%
  layout(
    #title = "Time Series of ibp & JORN.00042",
   # xaxis = list(title='Date'),
    xaxis = list(
        type = 'date',
        tickformat = " %B<br>%Y", 
        title='Date'),
        
        yaxis = list(
          title = 'USA-NPN Status Intensity',
          typeformat='%', 
          nticks=6,
          tick0=0,
          dtick=25,
          ticktext=xscale
          # tick0=5,
          # dtick=25, 
          # tick
          #range=c(0,100))
        # yaxis = list(
        # range=c(0,100))
  ))

p2
```